---
title: "P8105 Homework 6"
author: "Quinton Neville"
date: "November 20, 2018"
header-includes: 
  \usepackage{graphicx}
  \usepackage{float}
  \usepackage{amsmath}
output:
   github_document
---

```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
#Load necessary packages
library(tidyverse)
library(readxl)
library(readr)
library(p8105.datasets)
library(patchwork)
library(ggridges)
library(gridExtra)
library(shiny)
library(plotly)
library(broom)
library(scales)
library(purrr)
library(koRpus)
library(modelr)

#Controlling figure output in markdown
knitr::opts_chunk$set(
#  fig.height =   
  fig.width = 6,
#  fig.asp = .5,
  out.width = "90%",
#  out.height = 
 fig.align = "center",
  cache = FALSE
)

#Set Theme for ggplot2
theme_set(theme_bw() + theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom"))

#Set Scientific notation output for knitr
options(scipen = 999)

```

#Problem 1

This problem concerns previously investigated data concerning the rate of homocide resolution in police departements in major cities around the country. Here, we will briefly clean and tidy these data and fit GLM logit models by city on unsolved with victim age, sex, and race as predictors, focusing on the coefficient for race, obtain 95% CI's for these coefficient estimates, and visualize the results. 

####Read and Clean Washington Post Data
```{r problem_2, warning = FALSE, error = FALSE, message = FALSE}
#Read in the wp homicide data
wp.homicide.df <- read_csv("./data/wp_homicide_data.csv")

#Snag Dimensions and summary
dim.wp.df <- dim(wp.homicide.df)

#Unique City/State locations
unique.locations <- wp.homicide.df %>% distinct(., city, state) %>% nrow() 

#New city_state variable, filtering, and mutating
wp.homicide.df <- wp.homicide.df %>%
  mutate(
    city_state = str_c(city, state, sep = ", "), 
    unsolved = ifelse(disposition == "Closed without arrest" | disposition == "Open/No arrest", TRUE, FALSE)
  ) %>% select(city_state, everything()) %>%
  filter(city_state != "Dallas, TX" & city_state != "Phoenix, AZ" &
         city_state != "Kansas City, MO" & city_state != "Tulsa, AL") %>%
  mutate(
    victim_race = ifelse(victim_race == "White", "white", "non-white"), 
    victim_race = as.factor(victim_race) %>% fct_relevel(., "white", "non-white"),
    victim_age = parse_number(victim_age)
  )
```

####Fit a Logit GLM for Baltimore, MD
Here, we fit a GLM from the binomial family, with the binary solved or unsolved variable as the response and victim age, sex, and race as predictors. We then obtained a 95% CI for the estimated coefficient for race, describing the change in log odds of the case being unsolved. Lastly, we produce a table of the exponentiated values, back transforming out of log-space to interpret the coefficients in terms of odds. 
```{r warning = FALSE, error = FALSE}
#GLM model Baltimore
baltimore.glm <- wp.homicide.df %>% group_by(city_state) %>% nest() %>% filter(city_state == "Baltimore, MD") %>%
  mutate(glm_model = map(data, ~glm(unsolved ~ victim_age + victim_sex + victim_race, data = .x, family = "binomial")),
         conf_int = map(.x = glm_model, ~confint_tidy(.x, conf.level = 0.95)),
         glm_model = map(glm_model, ~broom::tidy(.x))) %>%
  unnest(., glm_model, conf_int) %>%
  filter(term == "victim_racenon-white") %>%
  select(city_state, estimate, conf.low, conf.high) %>%
  gather(key = type, value = value, estimate:conf.high) %>%
  mutate(value = exp(value))

baltimore.glm %>% knitr::kable()
```

The table obtained above describes that in Baltimore, MD, we would expect to see a 127% increase in the odds of a homocide being unsolved if the victim was not-white, after adjusting for victim age and sex. The corresponding 95% CI implies that we are 95% confident that the true odds ratio for non-white victim homocide resolution in Baltimore, MD lies between (1.61, 3.2). As this does not include 1, we have good evidence to suggest there is a significant increase in the odds of a homocide case being unsolved when the victim is non-white in Baltimore, MD, after adjusting for victim age and sex.


####Repeat GLM Modeling for All Cities

We repeat the process outlined above for each city in these data. Again we fit the glm, obtain a 95% confidence interval for the coefficient estimate, exponetial transform to obtain the OR, and manipulate the resulting data frame for visualization. 
```{r warning = FALSE, error = FALSE}
#GLM all Cities
all.city.glm <- wp.homicide.df %>% group_by(city_state) %>% nest() %>%
  mutate(glm_model = map(data, ~glm(unsolved ~ victim_age + victim_sex + victim_race, data = .x, family = "binomial")),
         conf_int = map(.x = glm_model, ~confint_tidy(.x, conf.level = 0.95)),
         glm_model = map(glm_model, ~broom::tidy(.x))) %>%
  unnest(., glm_model, conf_int) %>%
  filter(term == "victim_racenon-white") %>%
  select(city_state, estimate, conf.low, conf.high) %>%
  mutate(city_state = as.factor(city_state) %>% fct_reorder(., estimate, .desc = FALSE)) %>%
  gather(key = type, value = value, estimate:conf.high) %>%
  mutate(value = exp(value)) %>%
  spread(type, value)
```

Here we visualize the resulting OR for a homocide being unsolved for non-white victims in each city, after adjusting for victim age and sex. Cities are found on the y-axis, OR are on the x-axis, and the red error bars describe the 95% confidence interval for the true OR. 

```{r fig.width = 6, fig.height = 10}
all.city.glm %>%
  ggplot(aes(x = city_state, y = estimate, fill = estimate)) +
  geom_bar(stat = "identity", colour = "black", width = 1, alpha = 0.9) +
  geom_errorbar(aes(x = city_state, ymin = conf.low, ymax = conf.high), colour = "red", size = .9, alpha = 0.5) +
  coord_flip() +
  viridis::scale_fill_viridis(
    option = "magma",
    name = "Odds Ratio", 
    discrete = FALSE
  ) +
  labs(
    x = "City",
    y = "Odds Ratio",
    title = "Odds of Unsolved Homocide for Non-White Victims"
  ) +
    theme(legend.position = "bottom",
        axis.text.y = element_text(color = "black", 
        size = 10,  hjust = 1) ) +
  scale_y_continuous(breaks = seq(0, 24, 1), sec.axis = dup_axis())
```

With respect to the visualization above, it is important to note that while all 95% CI's do not contain 1, almost every estimated coefficient is above 1. Remark on how many have CI lower bounds above 1, and  the max case. Conclude with evidence to suggest race is a meaningful factor in homocide resoution in many US cities. 

#Problem 2

```{r message = FALSE}
child.bw.df <- read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    babysex = ifelse(babysex == 1, "Male", "Female") %>% as.factor(),
    frace = as.factor(frace),
    mrace = as.factor(mrace),
    malform = ifelse(malform == 1, TRUE, FALSE)
  ) %>%
  select(bwt, everything())

#Check NA
missing_vec <- apply(child.bw.df, 2, function(x) {sum(is.na(x))})
```

####Modeling
```{r results = 'hide'}
#Subset LM Selection (AIC)
mult.fit <- lm(bwt ~ ., data = child.bw.df)
back.sub.formula <- step(mult.fit, direction = 'backward')$terms
back.sub.mod <- lm(back.sub.formula, data = child.bw.df) 
```

```{r}
back.sub.mod %>% broom::tidy() %>%
  knitr::kable()
```

```{r}
child.bw.df %>%
  add_residuals(back.sub.mod) %>%
  add_predictions(back.sub.mod) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  labs(
    x = "Fitted",
    y = "Residual",
    title = "Residuals vs. Fitted"
  )
```


####Comparing Models

Given our selected model above, we will fit two alternative linear models for birthweight 
- Baby length at birth and gestational age as predictors
- Baby head circumference, length at birth, and sex; using all possible interactions.

We will compare our model with these two alternatives using 10-fold Cross validation with MSE as the predictive quantity to minimize. 
```{r}
mod.2a <- child.bw.df %>% lm(bwt ~ blength + gaweeks, data = .)
mod.2a %>% broom::tidy() %>% knitr::kable()

mod.2b <- child.bw.df %>% lm(bwt ~ bhead * babysex + bhead * blength + blength * babysex + bhead * babysex * blength, data = .)
mod.2b %>% broom::tidy() %>% knitr::kable()
```


```{r}
cv.df <- crossv_mc(child.bw.df, 100) %>%
  mutate(train = map(train, as.tibble),
         test = map(test, as.tibble)) %>%
  mutate(back_sub_lm = map(train, ~lm(back.sub.formula, data = .x)),
         lm_2a = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         lm_2b = map(train, 
                     ~lm(bwt ~ bhead * babysex + bhead * blength + blength * babysex + bhead * babysex * blength, data = .x))) %>%
  mutate(back_sub_rmse = map2_dbl(back_sub_lm, test, ~rmse(model = .x, data = .y)),
         lm_2a_rmse = map2_dbl(lm_2a, test, ~rmse(model = .x, data = .y)),
         lm_2b_rmse = map2_dbl(lm_2b, test, ~rmse(model = .x, data = .y)))
  
cv.df %>% 
  select(ends_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "_rmse", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() + 
  geom_boxplot(width = 0.25) +
  labs(
    x = "Root Mean Sqaure Error",
    y = "Model",
    title = "RMSE by Model"
  )
```