---
title: "P8105 Homework 6"
author: "Quinton Neville"
date: "November 20, 2018"
header-includes: 
  \usepackage{graphicx}
  \usepackage{float}
  \usepackage{amsmath}
output:
   github_document
---

```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
#Load necessary packages
library(tidyverse)
library(readxl)
library(readr)
library(p8105.datasets)
library(patchwork)
library(ggridges)
library(gridExtra)
library(shiny)
library(plotly)
library(broom)
library(scales)
library(purrr)
library(koRpus)
library(modelr)

#Controlling figure output in markdown
knitr::opts_chunk$set(
#  fig.height =   
  fig.width = 6,
#  fig.asp = .5,
  out.width = "90%",
#  out.height = 
 fig.align = "center",
  cache = FALSE
)

#Set Theme for ggplot2
theme_set(theme_bw() + theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom"))

#Set Scientific notation output for knitr
options(scipen = 999)

```

#Problem 1

```{r problem_2, warning = FALSE, error = FALSE, message = FALSE}
#Read in the wp homicide data
wp.homicide.df <- read_csv("./data/wp_homicide_data.csv")

#Snag Dimensions and summary
dim.wp.df <- dim(wp.homicide.df)

#Unique City/State locations
unique.locations <- wp.homicide.df %>% distinct(., city, state) %>% nrow() 

#New city_state variable, filtering, and mutating
wp.homicide.df <- wp.homicide.df %>%
  mutate(
    city_state = str_c(city, state, sep = ", "), 
    unsolved = ifelse(disposition == "Closed without arrest" | disposition == "Open/No arrest", TRUE, FALSE)
  ) %>% select(city_state, everything()) %>%
  filter(city_state != "Dallas, TX" & city_state != "Phoenix, AZ" &
         city_state != "Kansas City, MO" & city_state != "Tulsa, AL") %>%
  mutate(
    victim_race = ifelse(victim_race == "White", "white", "non-white"), 
    victim_race = as.factor(victim_race) %>% fct_relevel(., "white", "non-white"),
    victim_age = parse_number(victim_age)
  )
```

```{r warning = FALSE, error = FALSE}
#GLM model Baltimore
baltimore.glm <- wp.homicide.df %>% group_by(city_state) %>% nest() %>% filter(city_state == "Baltimore, MD") %>%
  mutate(glm_model = map(data, ~glm(unsolved ~ victim_age + victim_sex + victim_race, data = .x, family = "binomial")),
         conf_int = map(.x = glm_model, ~confint_tidy(.x, conf.level = 0.95)),
         glm_model = map(glm_model, ~broom::tidy(.x))) %>%
  unnest(., glm_model, conf_int) %>%
  filter(term == "victim_racenon-white") %>%
  select(city_state, estimate, conf.low, conf.high) %>%
  gather(key = type, value = numeric, estimate:conf.high) %>%
  mutate(numeric = exp(numeric))

#GLM all Cities
all.city.glm <- wp.homicide.df %>% group_by(city_state) %>% nest() %>%
  mutate(glm_model = map(data, ~glm(unsolved ~ victim_age + victim_sex + victim_race, data = .x, family = "binomial")),
         conf_int = map(.x = glm_model, ~confint_tidy(.x, conf.level = 0.95)),
         glm_model = map(glm_model, ~broom::tidy(.x))) %>%
  unnest(., glm_model, conf_int) %>%
  filter(term == "victim_racenon-white") %>%
  select(city_state, estimate, conf.low, conf.high) %>%
  mutate(city_state = as.factor(city_state) %>% fct_reorder(., estimate, .desc = FALSE)) %>%
  gather(key = type, value = numeric, estimate:conf.high) %>%
  mutate(numeric = exp(numeric)) %>%
  spread(type, numeric)

```

```{r fig.width = 6, fig.height = 10}
all.city.glm %>%
  ggplot(aes(x = city_state, y = estimate, fill = estimate)) +
  geom_bar(stat = "identity", colour = "black", width = 1, alpha = 0.9) +
  geom_errorbar(aes(x = city_state, ymin = conf.low, ymax = conf.high), colour = "red", size = .9, alpha = 0.5) +
  coord_flip() +
  viridis::scale_fill_viridis(
    option = "magma",
    name = "Multiplicative Odds Increase", 
    discrete = FALSE
  ) +
  labs(
    x = "City",
    y = "Multiplicative Odds Increase",
    title = "Odds of Homocide Unsolved for Non-White Victims"
  ) +
    theme(legend.position = "bottom",
        axis.text.y = element_text(color = "black", 
        size = 10,  hjust = 1) ) +
  scale_y_continuous(breaks = seq(0, 24, 1), sec.axis = dup_axis())
```



#Problem 2

```{r message = FALSE}
child.bw.df <- read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    babysex = ifelse(babysex == 1, "Male", "Female") %>% as.factor(),
    frace = as.factor(frace),
    mrace = as.factor(mrace),
    malform = ifelse(malform == 1, TRUE, FALSE)
  ) %>%
  select(bwt, everything())

#Check NA
missing_vec <- apply(child.bw.df, 2, function(x) {sum(is.na(x))})
```

####Modeling
```{r results = 'hide'}
#Subset LM Selection (AIC)
mult.fit <- lm(bwt ~ ., data = child.bw.df)
back.sub.formula <- step(mult.fit, direction = 'backward')$terms
back.sub.mod <- lm(back.sub.formula, data = child.bw.df) 
```

```{r}
back.sub.mod %>% broom::tidy() %>%
  knitr::kable()
```

```{r}
child.bw.df %>%
  add_residuals(back.sub.mod) %>%
  add_predictions(back.sub.mod) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  labs(
    x = "Fitted",
    y = "Residual",
    title = "Residuals vs. Fitted"
  )
```


####Comparing Models

Given our selected model above, we will fit two alternative linear models for birthweight 
- Baby length at birth and gestational age as predictors
- Baby head circumference, length at birth, and sex; using all possible interactions.

We will compare our model with these two alternatives using 10-fold Cross validation with MSE as the predictive quantity to minimize. 
```{r}
mod.2a <- child.bw.df %>% lm(bwt ~ blength + gaweeks, data = .)
mod.2a %>% broom::tidy() %>% knitr::kable()

mod.2b <- child.bw.df %>% lm(bwt ~ bhead * babysex + bhead * blength + blength * babysex + bhead * babysex * blength, data = .)
mod.2b %>% broom::tidy() %>% knitr::kable()
```


```{r}
cv.df <- crossv_mc(child.bw.df, 100) %>%
  mutate(train = map(train, as.tibble),
         test = map(test, as.tibble)) %>%
  mutate(back_sub_lm = map(train, ~lm(back.sub.formula, data = .x)),
         lm_2a = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         lm_2b = map(train, 
                     ~lm(bwt ~ bhead * babysex + bhead * blength + blength * babysex + bhead * babysex * blength, data = .x))) %>%
  mutate(back_sub_rmse = map2_dbl(back_sub_lm, test, ~rmse(model = .x, data = .y)),
         lm_2a_rmse = map2_dbl(lm_2a, test, ~rmse(model = .x, data = .y)),
         lm_2b_rmse = map2_dbl(lm_2b, test, ~rmse(model = .x, data = .y)))
  
cv.df %>% 
  select(ends_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "_rmse", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() + 
  geom_boxplot(width = 0.25) +
  labs(
    x = "Root Mean Sqaure Error",
    y = "Model",
    title = "RMSE by Model"
  )
```